Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Include explanation of terms in momentum and energy equations.

\noindent and is solved for the time-dependent uniform fluid velocity $V_z$ through the bed.

@@

@@

\noindent while the energy equation for the solid phase is written as:

@@

\colorbox{yellow}{Fabio, talvez valha a pena explicar quem eh quem nos termos das equacoes da Q movimento e energias...}

>>>>

\noindent where the macroscopic inertial term on the left-hand side is balanced with the pressure gradient, Darcy stress and Forchheimer drag \cite{bib:nield06_convec_porous_media}. The momentum equation is solved for the time-dependent uniform fluid velocity $V_z$ through the bed.

@@

\noindent where the left-hand side includes the inertial and advection terms, and the right-hand side includes terms for the solid-fluid heat transfer, viscous dissipation, heat conduction, porous-media dispersion, and casing losses.

@@

The energy equation for the solid phase is written as:

@@

\noindent where the terms represent respectively inertia, solid-fluid heat transfer and heat conduction.
